FraCaS: 80 percent complete

### 2019-02-11 paper2018/paper.tex
intro additions

\section{Introduction}

>>>>

\section{Introduction}
Natural Language Inference (NLI) is task of determining of whether an NL hypothesis H follows from an NL premise(s) P. NLI has received a lot of attention in the Computational Semantics literature and has been approached using a variety of techniques, ranging from logical approaches  \citet{bos:2008,Mineshima:2015,Abzianidze:2015,bernardy_type_2017} all the way to the recent Deep Learning (DL) models for NLP.
